### 2016-05-19 2016-lrec-tyvmorph/poster.tex
some more work on the latex poster
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@68624 72bbbca6-d526-0410-a7d9-f06f51895060

\usepackage{tikz}
\usetikzlibrary{shapes,arrows} %for flowchart
% Define block styles
\newcommand{\flowchartscale}{0.65}
\tikzstyle{decision} = [diamond, draw, fill=iumint, 
    text width=5em, text badly centered, node distance=3cm, inner sep=0pt,
	 font=\diagsans, scale=\flowchartscale]
\tikzstyle{block} = [rectangle, draw, fill=iulimestone, 
    text width=5em, text centered, rounded corners, minimum height=4em,
	 font=\diagsans, scale=\flowchartscale]
\tikzstyle{line} = [draw, -latex', thick, font=\diagsans]
\tikzstyle{cloud} = [draw, ellipse,fill=iumidnight, text=grey, text width=8em,
	text centered, %node distance=3cm,
	minimum height=2em, font=\diagsans, scale=\flowchartscale]
%\usepackage{pgfbaselayers}
%\pgfdeclarelayer{background}
%\pgfdeclarelayer{foreground}
%\pgfsetlayers{background,main,foreground}

@@

		\headerbox{Development cycle}{name=development,below=morphtrans}{
			\begin{tikzpicture}[xscale=1.92,yscale=2.65]%, auto]

				\node[cloud] (assumptions) at (1,2.75) {assumed generalisations};
				\node[block] (compile) at (1,2) {compile analyser};
				\node[block] (analyse) at (1,1.5) {analyse corpus};
				\node[block] (check) at (1,1) {examine freq.\ list};
				\node[decision] (missingstem) at (1,0) {missing stem?};
				\node[block] (addstem) at (0.22,2) {add stem};
				\node[decision] (phonormorph) at (2,0) {type of problem?};
				\node[block] (updatephon) at (3,0) {update phonol.};
				\node[block] (updatemorph) at (3,1) {update morphol.};
				\node[decision] (phonbetter) at( 4,0) {better?};
				\node[decision] (morphbetter) at (4,1) {better?};
				\node[cloud] (newgeneralisation) at (2.5,2) {new\\grammatical\\generalisation};

				\path[line] (assumptions) -- node [right=0.75ex, align=left, scale=\flowchartscale] {preliminary\\development} (compile);
				\path[line] (compile) -- (analyse);
				\path[line] (analyse) -- (check);
				\path[line] (check) -- node [right=0.75ex, scale=\flowchartscale, align=left] {unanalysed\\forms} (missingstem);
				\path[line] (missingstem) -| node [below=1ex, near start, scale=\flowchartscale] {yes} (addstem);
				\path[line] (addstem) -- (compile);
				\path[line] (missingstem) -- node [below=1ex, midway, scale=\flowchartscale] {no} (phonormorph);
				\path[line] (phonormorph) -- node [below=1ex, near start, scale=\flowchartscale] {phon} (updatephon);
				\path[line] (phonormorph) |- node [below=1ex, near end, scale=\flowchartscale] {morph} (updatemorph);
				\path[line] (updatephon) -- node [above=0.5ex, scale=\flowchartscale, align=center] {diff \\ freq \\ list} (phonbetter) ;
				\path[line] (updatemorph) -- node [above=0.5ex, scale=\flowchartscale, align=center] {diff \\ freq \\ list} (morphbetter) ;
				\path[line] (phonbetter.east) -- node [below=1ex, near start, scale=\flowchartscale] {yes} (4.6,0) |- (newgeneralisation.east) ;
				\path[line] (morphbetter.east) -- node [below=1ex, near start, scale=\flowchartscale] {yes} (4.6,1) |- (newgeneralisation.east) ;
				\path[line] (phonbetter.north) |- node [right=1ex, near start, scale=\flowchartscale] {no} (4,0.5) -| (updatephon.north) ;
				\path[line] (morphbetter.north) |- node [right=1ex, near start, scale=\flowchartscale] {no} (4,1.5) -| (updatemorph.north) ;
				\path[line] (newgeneralisation) -- (compile);

			\end{tikzpicture}%}

@@

	\headerbox{Evaluation}{name=results,column=1,below=example}{

@@

		\headerbox{Ongoing and future work}{name=nedostatki,column=2,below=example}{
		\htwo{our other Turkic-language transducers}
		\begin{itemize}
			%\item Turkish (\hiliteone{Çöltekin, 2010 \& 2014}; \hilitetwo{Oflazer, 1994})
			%\item Crimean Tatar (\hilitetwo{Altıntaş, 2001})
			%\item Turkmen (\hilitetwo{Tantuğ et al., 2006})
			%\item Kazakh (\hilitetwo{Бекманова \& Махимов, 2013})
			%\vspace{1pt}\hfill{} \hiliteone{GPL (=free and open)}!
			%\item our Kyrgyz, Kazakh, Tatar, Kumyk:\ all \hiliteone{GPL (=free and open)}!
			\item Kyrgyz \parencite{jnwmifmt2012lrecpaper}%  (Washington et al., 2012)
			\item Tatar \& Bashkort \parencite{fmtjnwisrb2012lrecpaper} %(Tyers et al., 2012)
			\item Kazakh \parencite{isjnwfmt2013mtsummitpaper} %(Salimzyanov et al., 2013)
			\item Kumyk \parencite{jnwisfmt2014lrecpaper} %(Washington et al., 2014)
			\item ongoing work on Sakha, Khakas, and more!
		\end{itemize}
		\dividerspace{}

>>>>

\usepackage{tikz}
\usetikzlibrary{shapes,arrows} %for flowchart
% Define block styles
\newcommand{\flowchartscale}{0.85}
\tikzstyle{decision} = [diamond, draw, fill=iumint, 
    text width=5em, text badly centered, node distance=3cm, inner sep=0pt,
	 font=\diagsans, scale=\flowchartscale]
\tikzstyle{block} = [rectangle, draw, fill=iulimestone, 
    text width=5em, text centered, rounded corners, minimum height=4em,
	 font=\diagsans, scale=\flowchartscale]
\tikzstyle{line} = [draw, -latex', thick, font=\diagsans]
\tikzstyle{cloud} = [draw, ellipse,fill=iumidnight, text=grey, text width=8em,
	text centered, %node distance=3cm,
	minimum height=2em, font=\diagsans, scale=\flowchartscale]
%\usepackage{pgfbaselayers}
%\pgfdeclarelayer{background}
%\pgfdeclarelayer{foreground}
%\pgfsetlayers{background,main,foreground}

@@

		\headerbox{Development cycle}{name=development,below=morphtrans,span=2}{
		\centering
		\begin{tikzpicture}[xscale=3,yscale=2.8]%, auto]

			\node[cloud] (assumptions) at (1,2.75) {assumed generalisations};
			\node[block] (compile) at (1,2) {compile analyser};
			\node[block] (analyse) at (1,1.4) {analyse corpus};
			\node[block] (check) at (1,0.7) {examine freq.\ list};
			\node[decision] (missingstem) at (1,0) {missing stem?};
			\node[block] (addstem) at (0,2) {add stem};
			\node[decision] (phonormorph) at (2.25,0) {type of problem?};
			\node[block] (updatephon) at (3.5,0) {update phonol.};
			\node[block] (updatemorph) at (3.5,1) {update morphol.};
			\node[decision] (phonbetter) at(5,0) {better?};
			\node[decision] (morphbetter) at (5,1) {better?};
			\node[cloud] (newgeneralisation) at (3,2) {new\\grammatical\\generalisation};

			\path[line] (assumptions) -- node [right=0.75ex, align=left, scale=\flowchartscale] {initial\\development} (compile);
			\path[line] (compile) -- (analyse);
			\path[line] (analyse) -- node [right=0.75ex, scale=\flowchartscale, align=left] {unanalysed\\forms} (check);
			\path[line] (check) -- (missingstem);
			\path[line] (missingstem) -| node [below=1ex, near start, scale=\flowchartscale] {yes} (addstem);
			\path[line] (addstem) -- (compile);
			\path[line] (missingstem) -- node [below=1ex, midway, scale=\flowchartscale] {no} (phonormorph);
			\path[line] (phonormorph) -- node [below=1ex, near start, scale=\flowchartscale] {phon} (updatephon);
			\path[line] (phonormorph) |- node [below=1ex, near end, scale=\flowchartscale] {morph} (updatemorph);
			\path[line] (updatephon) -- node [above=0.5ex, scale=\flowchartscale, align=center] {diff \\ freq list} (phonbetter) ;
			\path[line] (updatemorph) -- node [above=0.5ex, scale=\flowchartscale, align=center] {diff \\ freq list} (morphbetter) ;
			\path[line] (phonbetter.east) -- node [below=1ex, near start, scale=\flowchartscale] {yes} (5.6,0) |- (newgeneralisation.east) ;
			\path[line] (morphbetter.east) -- node [below=1ex, near start, scale=\flowchartscale] {yes} (5.6,1) |- (newgeneralisation.east) ;
			\path[line] (phonbetter.north) |- node [right=1ex, near start, scale=\flowchartscale] {no} (5,0.5) -| (updatephon.north) ;
			\path[line] (morphbetter.north) |- node [right=1ex, near start, scale=\flowchartscale] {no} (5,1.5) -| (updatemorph.north) ;
			\path[line] (newgeneralisation) -- (compile);

		\end{tikzpicture}
%			\begin{tikzpicture}[xscale=1.92,yscale=2.65]%, auto]	
%
%				\node[cloud] (assumptions) at (1,2.75) {assumed generalisations};
%				\node[block] (compile) at (1,2) {compile analyser};
%				\node[block] (analyse) at (1,1.5) {analyse corpus};
%				\node[block] (check) at (1,1) {examine freq.\ list};
%				\node[decision] (missingstem) at (1,0) {missing stem?};
%				\node[block] (addstem) at (0.22,2) {add stem};
%				\node[decision] (phonormorph) at (2,0) {type of problem?};
%				\node[block] (updatephon) at (3,0) {update phonol.};
%				\node[block] (updatemorph) at (3,1) {update morphol.};
%				\node[decision] (phonbetter) at( 4,0) {better?};
%				\node[decision] (morphbetter) at (4,1) {better?};
%				\node[cloud] (newgeneralisation) at (2.5,2) {new\\grammatical\\generalisation};
%
%				\path[line] (assumptions) -- node [right=0.75ex, align=left, scale=\flowchartscale] {preliminary\\development} (compile);
%				\path[line] (compile) -- (analyse);
%				\path[line] (analyse) -- (check);
%				\path[line] (check) -- node [right=0.75ex, scale=\flowchartscale, align=left] {unanalysed\\forms} (missingstem);
%				\path[line] (missingstem) -| node [below=1ex, near start, scale=\flowchartscale] {yes} (addstem);
%				\path[line] (addstem) -- (compile);
%				\path[line] (missingstem) -- node [below=1ex, midway, scale=\flowchartscale] {no} (phonormorph);
%				\path[line] (phonormorph) -- node [below=1ex, near start, scale=\flowchartscale] {phon} (updatephon);
%				\path[line] (phonormorph) |- node [below=1ex, near end, scale=\flowchartscale] {morph} (updatemorph);
%				\path[line] (updatephon) -- node [above=0.5ex, scale=\flowchartscale, align=center] {diff \\ freq \\ list} (phonbetter) ;
%				\path[line] (updatemorph) -- node [above=0.5ex, scale=\flowchartscale, align=center] {diff \\ freq \\ list} (morphbetter) ;
%				\path[line] (phonbetter.east) -- node [below=1ex, near start, scale=\flowchartscale] {yes} (4.6,0) |- (newgeneralisation.east) ;
%				\path[line] (morphbetter.east) -- node [below=1ex, near start, scale=\flowchartscale] {yes} (4.6,1) |- (newgeneralisation.east) ;
%				\path[line] (phonbetter.north) |- node [right=1ex, near start, scale=\flowchartscale] {no} (4,0.5) -| (updatephon.north) ;
%				\path[line] (morphbetter.north) |- node [right=1ex, near start, scale=\flowchartscale] {no} (4,1.5) -| (updatemorph.north) ;
%				\path[line] (newgeneralisation) -- (compile);
%			\end{tikzpicture}%}

@@

	\headerbox{Lexicon}{name=lexicon,column=1,below=example}{
		\begin{tabular}{llr}
			\toprule
			Part of speech	&	Tag	& Stems \\
			\midrule
			Noun & \tag{n} & 4,226 \\
			Proper noun & \tag{np} & 4,217 \\
			Adjective & \tag{adj} & 1,603 \\
			Verb & \tag{v} & 1,064 \\
			Adverb & \tag{adv} & 136 \\
			Numeral & \tag{num} & 85 \\
			Conjunction & \tag{cnj*} & 70 \\
			Postposition & \tag{post} & 28 \\
			Pronoun & \tag{prn} & 35 \\
			Determiner & \tag{det} & 26 \\
			\midrule
			Total &  & 11,490 \\
			\bottomrule
		\end{tabular}
	}

	\headerbox{Evaluation}{name=results,column=1,below=lexicon}{

@@

		\headerbox{Ongoing and future work}{name=nedostatki,column=2,below=example}{
		\htwo{our other Turkic-language transducers}
		\begin{itemize}
			%\item Turkish (\hiliteone{Çöltekin, 2010 \& 2014}; \hilitetwo{Oflazer, 1994})
			%\item Crimean Tatar (\hilitetwo{Altıntaş, 2001})
			%\item Turkmen (\hilitetwo{Tantuğ et al., 2006})
			%\item Kazakh (\hilitetwo{Бекманова \& Махимов, 2013})
			%\vspace{1pt}\hfill{} \hiliteone{GPL (=free and open)}!
			%\item our Kyrgyz, Kazakh, Tatar, Kumyk:\ all \hiliteone{GPL (=free and open)}!
			\item \textbf{Kyrgyz} \parencite{jnwmifmt2012lrecpaper}%  (Washington et al., 2012)
			\item \textbf{Tatar} \& \textbf{Bashkort} \parencite{fmtjnwisrb2012lrecpaper} %(Tyers et al., 2012)
			\item \textbf{Kazakh} \parencite{isjnwfmt2013mtsummitpaper} %(Salimzyanov et al., 2013)
			\item \textbf{Kumyk} \parencite{jnwisfmt2014lrecpaper} %(Washington et al., 2014)
			\item ongoing work on Sakha, Khakas, and more!
		\end{itemize}
		\dividerspace{}

		\htwo{Morphological disambiguation}
		\begin{itemize}
			\item \textbf{Kazakh} \parencite{zajnwftanasakbada2016ciclingproceedings}
		\end{itemize}
		\dividerspace{}

		\htwo{Treebanks}
		\vspace{-1em}
		\newline
			\tikzoverlay[text width=0.9\textwidth] at (0.55in, -0.5in) {
				\includegraphics[width=0.95\textwidth]{img/dep-graph}
			};
		\begin{itemize}
			\item \textbf{Kazakh} \parencite{fmtjnw2015kazdep}
		\end{itemize}
		\includegraphics[width=0.63\textwidth]{img/korp}
		\begin{itemize}
			\item work on \textbf{Tuvan} ongoing
		\end{itemize}
		\vspace{1.45in}
		\dividerspace{}
